Modeling thermal dust emission with two components: application to the {\it PLANCK} HFI maps

### 2014-09-14 ms.tex
less optimism about revised Planck zodi corrections

Imperfect zodiacal light (zodi) corrections represent a second major limitation
of our results. The ecliptic plane's prominence in our full-sky temperature map
(Figure \ref{fig:results}) suggests that the zodiacal light subtractions 
performed on the input maps are not ideal. Our comparisons of the FIR maps used
in this study against H\,\textsc{i} emission bear out this notion, further 
revealing that the imperfect zodi corrections are not limited to \verb|i100| 
(the map for which one would expect zodiacal contamination to be most 
problematic), but in fact are noticeable in all of the HFI 
\verb|R1.10_nominal_ZodiCorrected| maps as well. We deemed it infeasible to 
reconsider all of the \PLANCK~zodi corrections in addition to the 3000 GHz zodi
correction as a part of this study. Perhaps the forthcoming \PLANCK~data 
release, including observations acquired during additional orbits, will 
effectively eliminate any residual zodi problems in the \PLANCK~bands. Under 
these circumstances it might then be worthwhile to consider revising the DIRBE 
100$\mu$m zodi correction provided by SFD.

>>>>

Imperfect zodiacal light (zodi) corrections represent a second major limitation
of our results. The ecliptic plane's prominence in our full-sky temperature map
(Figure \ref{fig:results}) suggests that the zodiacal light subtractions 
performed on the input maps are not ideal. Our comparisons of the FIR maps used
in this study against H\,\textsc{i} emission bear out this notion, further 
revealing that the imperfect zodi corrections are not limited to \verb|i100| 
(the map for which one would expect zodiacal contamination to be most 
problematic), but in fact are noticeable in all of the HFI 
\verb|R1.10_nominal_ZodiCorrected| maps as well. We deemed it infeasible to 
reconsider all of the \PLANCK~zodi corrections in addition to the 3000 GHz zodi
correction as a part of this study, especially considering that the forthcoming
\PLANCK~2014 release is expected to include a revised/improved zodi 
subtraction.

%Perhaps the forthcoming \PLANCK~data 
%release, including observations acquired during additional orbits, will 
%effectively eliminate any residual zodi problems in the \PLANCK~bands. Under 
%these circumstances it might then be worthwhile to consider revising the DIRBE
%100$\mu$m zodi correction provided by SFD.
